### 2024-11-18 README.Rmd
custom averaging methods for textstat_embedding() and embed_docs()
Easy (down)loading for GloVe, fastText, word2vec, and ConceptNet models

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

@@

embeddingplyr won't help you train new embedding models, but it can load embeddings from a file. This is especially useful for pretrained word embedding models like GloVe and word2vec. These models can be downloaded (generally in txt or bin format, respectively) and loaded with `load_embeddings()`.

@@

glove_twitter_25d <- load_embeddings("~/Documents/data/glove/glove.twitter.27B.25d.txt")
```

@@

Given a tidy dataframe of texts, `embed_docs()` will generate embeddings by averaging the embeddings of words in each text (for more information on why this works well, see [Data Science for Psychology, Chapter 18](https://ds4psych.com/decontextualized-embeddings#sec-embedding-magnitude)).

>>>>

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
options(embeddings.model.path = "~/Documents/data/embeddings")
```

@@

embeddingplyr won't help you train new embedding models, but it can load embeddings from a file or download them from online. This is especially useful for pretrained word embedding models like GloVe, word2vec, and fastText. Dozens of these models can be conveniently downloaded from online sources with `load_embeddings()`.

@@

glove_twitter_25d <- load_embeddings("glove.twitter.27B.25d")
```

@@

Given a tidy dataframe of texts, `embed_docs()` will generate embeddings by averaging the embeddings of words in each text (for more information on why this works well, see [Data Science for Psychology, Chapter 18](https://ds4psych.com/decontextualized-embeddings#sec-embedding-magnitude)). By default, `embed_docs()` uses a simple unweighted mean, but other averaging methods are available.
